### 2014-07-03 research/paper/main/article.tex
3rd july

These two definitions show two important interpretations of the power with respect to any energy production device. The first shows that power will be high for situations where the damping coefficient is high, and the transverse velocity is consistently high. The second shows that power will be high for situations where the transverse force and the body velocity are in phase.

@@

 \input{../figure/uncollapsed_data}
  \input{../figure/collapsed_data}
 \subsection{Displacement, velocity and power}

@@

\subparagraph{limitation of the quasi-steady hypothesis at low Reynolds numbers}

Work done by \cite{Joly2012} has also been focused on the displacement of a body under galloping at low Reynolds numbers as well as at zero or minimal damping. Therefore studies were carried out analyse the behaviour of the velocity as the damping is increased. The quasi-steady results were compared with the DNS results. From the comparison it was found out that the discrepancy of the power output is quite high as \massdamp is increased.

>>>>

 \hilight{have to repharase} These two definitions show two important interpretations of the power with respect to any energy production device. The first shows that power will be high for situations where the damping coefficient is high, and the transverse velocity is consistently high. The second shows that power will be high for situations where the transverse force and the body velocity are in phase.

@@

 \input{../figure/uncollapsed_data}
  \input{../figure/collapsed_data}

 \subsection{Displacement, velocity and power}

@@

\subsection{limitation of the quasi-steady hypothesis at low Reynolds numbers}

The QSS hypothesis assumes that the only force driving the system is the instantaneous lift generated by the induced velocity. However, vortex shedding is also present in this system. Therefore, an essential assumption when this model is used is that the effect of vortex shedding is minimal. Hence, the model has been always used at high \reynoldsnumber and high mass ratios. The present study is focused on quantifying the limiting parameters of the QSS model at low Reynolds numbers by providing a comparison with DNS results.
